### 2020-03-30 reviews/SIGBOVIK_2020_review_13.tex
Assign COVID-19 review

%%%% The Proceedings Chair will fill in the following
%%%% two fields.
\papernum{NN}
\papertitle{UNKNOWN PAPER TITLE}

@@

%%% Replace the following text with your review.
\center\includegraphics[height=5in]{walk-to-sky-exp}

>>>>

%%%% The Proceedings Chair will fill in the following
%%%% two fields.
\papernum{36}
\papertitle{A thorough investigation of the degree to which the COVID-19 pandemic has enabled subpar-quality papers to make it into the proceedings of SIGBOVIK, by reducing the supply of authors willing to invest the necessary effort to produce high-quality papers}

@@

%%% Replace the following text with your review.
\vspace{-0.75in}
\center\includegraphics[height=4.25in]{walk-to-sky-exp}
